

\Abstract
Powered by the rise of cloud computing, agile development, DevOps and continuous deployment strategies, the microservice architectural pattern emerged as an alternative to monolithic software design. Microservices, as a suite of independent, highly cohesive and loosely coupled services, overcome the shortcoming of centralized monolithic architectures. Therefore, prominent companies recently migrated their monolithic legacy applications successfully to microservice-based architecture. The key challenge is to find an appropriate partition of legacy applications - namely \textit{microservice identification}. So far, the identification process is done intuitively based on the experience of system architects and software engineers, mainly by virtue of missing formal approaches and a lack of automated tool support. \\
However, when application grow in size and become progressively complex, it is quite demanding to decompose the system in appropriate microservices.
To tackle this challenge, the thesis provides a formal, graph-based identification approach using clustering techniques. Based on the business point of view, the approach uses control flow and data flow dependencies to build two weighted graphs. Clustering tools subsequently identify high cohesive sets of activities and data objects. Finally, those sets are matched to generate compound clusters of activities and corresponding data objects. Each cluster correspond to a microservice candidate. \\
An evaluation demonstrates that the approach identifies adequate microservices candidates that are similar to a manual decomposition, but identified with much less time expenditure and required expertise.


